A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-18 paper.tex
Done: Related Work

@@

C. Cornelis and G. Deschrijver \cite{cornelis2001compositional}
generalize the Compositional Rule of Inference to IFSs
%intuitionistic inference engine \cite{cornelis2001compositional} %Que
                                %diferencias hay?

A method for inference in approximate reasoning based on normal
intuitionistic fuzzy sets \cite{bustince1995method}

A Method and Electronic Circuit for Intuitionistic Fuzzy Inference
\cite{marinov2005method}
An intuitionistic fuzzy system for time series analysis in plant
monitoring and diagnosis \cite{castillo2007intuitionistic}

% Applications
Intuitionistic fuzzy sets in some medical applications
\cite{szmidt2001intuitionistic}
Switching between type-2 fuzzy sets and intuitionistic fuzzy sets: an
application in medical diagnosis \cite{own2009switching}
Intuitionistic preference relations and their application in group
decision making \cite{xu2007intuitionistic}
An application of intuitionistic fuzzy information for handwritten
Arabic word recognition \cite{baccour2008application}
Application of intuitionistic fuzzy sets, bacillus colonies
recognition \cite{davarzani2013novel}

% Por?  
%% (A): Porque es lo más cercano a un FIS mamdani intuicionista. al
%% menos de lo que encontré.

%%%%%%%%Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}

%%%%%%%%centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
%% Porque yo propongo una fórmula para calcular centroide de un IFS, y
%% como la competencia de un IFS sería un fuzzy set tipo 2, iba a
%% hablar un poco de eso

@@

The dataset consists of 100 data points for training, and 50 data
points for testing. These data points were scaled, such that the
resulting data points range from 0 to 100. The scaling process was
performed by applying (\ref{scaling}) over each of the data points in
the union of the training and testing subsets. The reason behind this
preprocessing is that the implementation of the IFIS works with inputs
ranging from 0 to 100, but the Mackey-Glass time series' data points
range from 0 to about 1.4. This does not alter the measurement of the
error produced by each of the FISs, as the outputs from the FISs are
also scaled from 0 to 100.

@@

Initially, 60 experiments were performed for every FIS, but that
number of experiments didn't provide enough statistical data for the
IT2-FISs in order to make a conclusion. For the IT2-FIS with uncertain
mean, 100 experiments were needed to provide enough statistical data
to conclude what FIS performed better, and for the IT2-FIS with
uncertain standard deviation, 300 experiments were needed. To clarify,
all of the comparisons were against the T1-IFIS.

Table \ref{first-hypothesis-tests-training} summarizes the results obtained
for each of the FISs in the training stage, as well as the t-value
obtained when calculating a Student's t-test. The same structure is
followed in Table \ref{first-hypothesis-tests-testing}, which shows the
results obtained for each of the FISs in the testing stage.

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, First Experiment}
  \label{first-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 89.50 & 25.36 & 60 &  & \\
    \hline
    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & > 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & > 99.9\% \\
    \hline
    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & > 99.9\% \\
    \hline
  \end{tabular}
\end{table}

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
  \label{second-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 76.22 & 16.90 & 400 & & \\
    \hline
    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & > 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & > 99.9\%\\
    \hline
    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & > 99.9\% \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, First Experiment}
  \label{first-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 160.99 & 65.70 & 60 &  & \\
    \hline
    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & > 99.2\%\\
    \hline
    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & > 97.8\% \\
    \hline
    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & > 91.4\% \\
    \hline
  \end{tabular}
\end{table}

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, Second Experiment}
  \label{second-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 139.38 & 95.75 & 400 &  &  \\
    \hline
    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & > 89.4\% \\
    \hline
    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & > 94.8\% \\
    \hline
    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & > 99.9\%\\
    \hline
  \end{tabular}
\end{table}

@@

>>>>

\usepackage{flushend}

@@

Implications using fuzzy sets can be extended to compositions of rules of
inference. A work that describes the compositional rule of inference
using fuzzy sets, and the extension of the compositional rule of
inference using IFSs, is the one by C. Cornelis and G. Deschrijver
\cite{cornelis2001compositional}.

H. Bustince et al. \cite{bustince1995method} propose a method to
perform inference using IFSs by using t-norm and t-conorm based on max
and min operators. This work resembles the foundations of a Mamdani
FIS. Another example is the work by M. Marinov and K. T. Atanassov
\cite{marinov2005method}, which implements an electronic circuit
capable of performing intuitionistic fuzzy inference, and describes
the computer pseudo-code that must be followed in order to implement
the method.

The closest to a Mamdani IFIS that the authors of this work could
find, was the work by O. Castillo et
al. \cite{castillo2007intuitionistic}. The authors implement an IFIS
by considering the membership functions and the non-membership
functions as traditional fuzzy sets. In the end, the output of the FIS
is calculated as a linear combination of the two fuzzy sets, by using
(\ref{linear-combination})

\begin{equation}
  \label{linear-combination}
  IFS = (1-\pi)FS_{\mu} + \pi FS_{v}
\end{equation}

The problem with this approach is that an IFS is being defined as two
separate traditional fuzzy sets, and the non-membership or the
indeterminacy is not affecting the membership of an element in a
meaningful way. In contrast, the present work proposes the use of the
intuitionistic membership in order to affect the firing strength that
will activate a consequent, and the use of the intuitionistic center
of area for obtaining a defuzzification of the aggregation of the
consequents.

Another proposal that is being made indirectly in this work, is the
way in which an IFS is represented. Most works represent an IFS as a
lattice (as in \cite{deschrijver2004representation} and
\cite{despi2013generalised}), but this work proposes a variation of the
standard way of representing a fuzzy set. Some works use
this way of representing an IFS (as in
\cite{davarzani2013novel}). The proposal in this paper is to use the
same convenient membership functions usually found in the design of
traditional FISs, such as triangular or Gaussian membership functions,
but using the complement of these functions to represent the
non-membership function.

The proposed method is tested by using the Mackey-Glass time series
benchmark, and therefore, an application of an IFIS is to use it for
forecasting tasks. Other fields where IFSs have been used are: medical
applications, as in the works by E. Szmidt and K. Janusz
\cite{szmidt2001intuitionistic}, H. Davarzani and
K. M. Amiri\cite{davarzani2013novel}, and C. M. Own
\cite{own2009switching}; group decision making, as in the work by
Z. Xu \cite{xu2007intuitionistic}; and handwritten word recognition,
as in the work by L. Baccour et al. \cite{baccour2008application}.

@@

The dataset consists of 500 data points for training, and 500 data
points for testing. These data points are ordered, as it is a time
series, and the first subset is for training and the second dataset is
for testing. These data points are scaled, such that the
resulting data points range from 0 to 100. The scaling process was
performed by applying (\ref{scaling}) over each of the data points in
the union of the training and testing subsets. The reason behind this
preprocessing is that the implementation of the IFIS works with inputs
ranging from 0 to 100, but the Mackey-Glass time series' data points
range from 0 to about 1.4. This does not alter the measurement of the
error produced by each of the FISs, as the outputs from the FISs are
also scaled from 0 to 100.

@@

A total of 400 runs were performed for every FIS. The decision for
such a high number of runs was because of trial and error. Initially,
the IFIS was being tested with a subset of the Mackey-Glass time
series of 100 points for training, and 50 for testing. This decision
was made as a consequence of the high computational time required to
process the traditional sizes of the subsets. Some of the
comparisons were successful, but others, especially against the
T2-FIS, were lacking statistical data in order to obtain a decisive
conclusion. In the end, the IT2-FIS with uncertain mean and the
IT2-FIS with uncertain standard deviation required a total of 100 and
300 runs, respectively. This led to the decision of performing 400
runs for each of the comparisons for the second experiment.

This first set of experiments used the same parameters
described in Section \ref{experiments}, and even though the dimensions
of the training and testing subsets of Mackey-Glass aren't the
traditional ones, the IFIS still achieved very good results. These
results can be found in Table \ref{first-hypothesis-tests-training}
and Table \ref{first-hypothesis-tests-testing}.

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, First Experiment}
  \label{first-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 89.50 & 25.36 & 60 &  & \\
    \hline
    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & $>$ 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & $>$ 99.9\% \\
    \hline
    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & $>$ 99.9\% \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, First Experiment}
  \label{first-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 160.99 & 65.70 & 60 &  & \\
    \hline
    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & $>$ 99.2\%\\
    \hline
    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & $>$ 97.8\% \\
    \hline
    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & $>$ 91.4\% \\
    \hline
  \end{tabular}
\end{table}

The second experiment follows exactly what is described in Section
\ref{experiments}, i.e., in comparison to the first experiment, both the
training dataset and testing dataset consist of 500 Mackey-Glass data
points. As has been stated before, this is the traditional practice
whet utilising the Mackey-Glass benchmark. Table
\ref{second-hypothesis-tests-training} summarizes the results obtained
for each of the FISs in the training stage, as well as the t-value
obtained when calculating a Student's t-test. CI in this case stands
for confidence interval. The same structure is followed in Table
\ref{second-hypothesis-tests-testing}, which shows the
results obtained for each of the FISs in the testing stage.

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
  \label{second-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 76.22 & 16.90 & 400 & & \\
    \hline
    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & $>$ 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & $>$ 99.9\%\\
    \hline
    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & $>$ 99.9\% \\
    \hline
  \end{tabular}
\end{table}

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, Second Experiment}
  \label{second-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 139.38 & 95.75 & 400 &  &  \\
    \hline
    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & $>$ 89.4\% \\
    \hline
    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & $>$ 94.8\% \\
    \hline
    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & $>$ 99.9\%\\
    \hline
  \end{tabular}
\end{table}

@@

In the training stage, every comparison achieved a confidence interval
greater than 99.9\%. Although the stage of most interest is the
testing stage, these results are still remarkable.

The only comparison which did not achieve a confidence interval
greater than 90\% was T1-IFIS vs. T1-FIS in the testing
stage. Nevertheless, the comparisons against the IT2-FIS with
uncertain mean and IT2-FIS with uncertain standard deviation achieved
high confidence intervals in this stage.
